PRIMUS: Quiescent Fraction as a Function of Environment and Redshift

### 2014-02-25 qfenv_paper/qf_environment.tex
Properly merged with home laptop

\title{PRIMUS: Quiescent Fraction as a Function of Environment and Redshift}
\author{ChangHoon Hahn, Michael Blanton, John Moustakas}

\begin{abstract}
We examine the evolution of the quiescent fraction, for galaxies in 
different density environments from $z=0.2-0.8$, using spectroscopic 
redshift and multi-wavelength imaging data from PRism MUlti-object 
Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). Using this 
data we construct a stellar mass limited target galaxy population of 
$40430$ galaxies from PRIMUS within redshift range $0.2-1.0$ and $106732$
galaxies from SDSS within redshift range $0.06-0.145$. This population 
is then classified as quiescent or star-forming using an evolving cut 
based on specific star-formation rate. The environment of the target 
population is then measured using a fixed cylindrical aperture method 
on a volume-limited {\em Environment Defining Population} constructed
from PRIMUS and SDSS.

Thresholds for the environment are imposed to classify the target galaxies as
high, mid, or low environments. For the quiescent and star-forming 
target galaxies we calculate the stellar mass functions in different environments and redshift.
Afterwards, we compute the quiescent fraction (QF) using the SMFs for the different environment 
and redshift ranges.  Comparing the QFs in these environment and redshift bins, we find the 
QF increases over time (decrease in redshift); however, the change of 
the QFs for the different environments are independent of the 
environment of galaxies. 
\end{abstract}

@@

@@

In all of the PRIMUS target fields we have near-UV (NUV) and far-UV (FUV) measurements from the {\em GALEX} Deep Imaging Survey (DIS; CITECITE ). 
To minimize contamination from neighboring sources, we use a Bayesian photometric code EM$_{\rm{PHOT}}$ (based on expectation maximization algorithm of CITECITE ). 
Furthermore, we use ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs in each of the fields to obtain integrated fluxes in all 
photometric bands.
To summarize, the general strategy employed is to use a circular aperture photometry to constrain the shape of the SED and then fixing the overall normalization to 
a estimate of the total magnitude in the detection band. 
\cite{Moustakas:2013aa} provides a detailed description of the calculation for each of our target fields.

From the spectroscopic redshift and photometry described above, we use \texttt{iSEDfit} to determine stellar masses, star formation rates (SFRs) and other physical properties
in a simplified Bayesian framework.
\texttt{iSEDfit}, which we will only briefly mention in this paper is discussed in detail in Appendix A of \cite{Moustakas:2013aa}.
The code uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. 
These generated model SEDs depend on population synthesis models and prior parameters.
In order to derive our fiducial stellar masses and star formation rates, we use the Flexible Stellar Population Synthesis (FSPS) models (CITECITE) based on the Chabrier (2003) IMF. 
Other prior parameters are listed in Section 4.1 of \cite{Moustakas}. 
The photometric bands we use for the fitting in our PRIMUS data are the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$, and the five optical bands
(in the COSMOS field, we fit seven optical bands and near-infrared bands, see Section 2.3 of \cite{Moustakas:2013aa}).
For a more detailed description of the data used in this paper, we refer readers to \cite{Moustakas:2013aa} Section 2 and Section 4.1.

\subsection{SDSS-GALEX} \label{sec:sdss}
For galaxies at low redshifts we use the SDSS Data Release 7 (DR7; CITECITE). 
From the SDSS DR7 data, which provides high fidelity $ugriz$ photometry and spectroscopic redshift, we specifically use galaxies from the New York University 
Value-Added Galaxy Catalog that satisfy the main sample criterion (CITECITE) and have galaxy extinction corrected (CITECITE) Petrosian magnitudes $14.5 < r < 17.6$ 
and spectroscopic redshits $0.01<z<0.2$. 
Within this sample, we select galaxies with medium depth observations from GALEX. 
This is done by first retrieving the positions of all {\em GALEX} tiles from GALEX Release 6 with total exposure time greater than $1$ ks and then constructing 
a joint angular selection function of the SDSS-{\em GALEX} Sample. 
This results in a final sample of $167,727$ SDSS galaxies with {\em GALEX} imaging.

For this final sample, we use the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diamater search radius to obtain the NUV and FUV photometry. 
For the optical photometry we use $ugriz$ bands (from the SDSS \texttt{model} magnitudes) scaled to the $r$-band \texttt{cmodel} magnitude. 
We supplement the above UV and optical photometry with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; CITECITE) and with photometry at $3.4$ 
and $4.6 \mu \rm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}. 
Further details on the photometry of the SDSS data used in this paper is provided in \cite{Moustakas:2013aa} Section 2.4.

To obtain the stellar masses and SFRs for the SDSS data, we use \texttt{iSEDfit} as done in Section \ref{sec:primus}. 
Except we use twelve photometric bands: {\em GALEX} FUV and NUV, SDSS $ugriz$, 2MASS $JHK_{s}$, and WISE $3.4$ and $4.6 \mu \rm{m}$.

\subsection{Galaxy Sample} \label{sec:target} 
In this seciton we will define the galaxy sample we use for our SMFs and QFs.
The population at intermediate redshift is derived from the PRIMUS data and the population at low redshift is derived from the SDSS data, both described above.
For the intermediate redshift target galaxy population, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for its parent sample.
We take the statistically complete {\em primary} sample from the PRIMUS data, \cite{Coil:2011aa}, and then we impose magnitude limits on optical selection bands as specified in 
\cite{Moustakas:2013aa} (listed in its Table 1).
These limits are in different optical selection bands and have different values for our five PRIMUS target fields.
Next, we join the PRIMUS, {\em GALEX}, and IRAC window functions to construct the angular selection function.
We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$) within the 
redshift range $0.2 - 1.0$.
Afterwards we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) to the objects in order to correct for targeting incompleteness and redshift 
failures.
The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
Equation 1 in \cite{Moustakas:2013aa}.
In addition to the selection criteria above, we impose stellar mass limits to have a stellar mass complete sample.  
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, apparent magnitude limit of the survey, and the typical stellar 
mass-to-light ratio of galaxies near the flux limit.

@@

For our target galaxy population at low redshift we use our SDSS-{\em GALEX} data. 
We limit our target population within the redshift range $0.06-0.145$ due to redshift limits later imposed for the volume-limited Environment Defining Population (\ref{sec:environment}).
The NYU-VAGC provides statistical weight estimates for targeting completeness.
In order to have a stellar mass complete low redshift target population, we use a uniform stellar mass limit of $10^9 \mathcal{M}_{odot}$, which is above the surface 
brightness and stellar mass-to-light ratio completness limits (CITECITE).
The absolute magnitude ($M_g$) versus redshift for the target galaxy population at both low redshift and intermediate redshift is plotted in Figure \ref{fig:targetEDP}.
We again refer readers to \cite{Moustakas:2013aa} for details; more specifically, Figure 2., Sections 3.1, and 4.3.

@@

In order to obtain the fixed aperture based environment for the galaxies in the target population, 
we first establish a volume limited {\it Environment Defining Population} (EDP) by imposing a fixed 
cumulative number density absolute magnitude cut off. 
\begin{table*} %Will contain much more information on environments. 
  \caption{Fixed Cylindrical Aperture Dimensions}
  \label{tab:aperture}
  \begin{center}
    \leavevmode
    \begin{tabular}{llllll} \hline \hline              
  Radius (Mpc)          &Height (Mpc)      &$n_{bin}$   &Edgecut &High Env Threshold (galaxies) &Low Env Threshold (galaxies) \\ \hline 
  1.0 &50 &6 & 80\% & 1.5 & 0.0          \\
  2.0 &50 &6 & 75\% & 4.0 & 0.0          \\ \hline
  \multicolumn{6}{l}{}                                             \\       
    \end{tabular}
  \end{center}
\end{table*}
The EDP for the PRIMUS sample is derived from the same parent sample as the target galaxies. 
We restrict the PRIMUS EDP galaxies within the redshift range $0.2-1.0$ and divide them into redshift bins of width $\Delta z = 0.2$. 
For each of these redshift bins, we impose separate absolute magnitude ($M_{g,\rm{lim}}$) limits such 
that the cumulative number density of the sample ordered by $M_{g}$ is equal to the cumulative 
number density of the highest redshift bin with an empirically determined limit. 
First, to determine the highest redshift bin ($0.8-1.0$) limit we look at the $M_{g}$ distribution with bin size
$\Delta M_{g} = 0.25$ and select $M_{g,\rm{lim}}$ to be the $M_{g}$ value near the peak of the 
distribution where number density of the bins with fainter objects (greater $M_{g}$ value) are smaller
than the number density of the bin at $M_{g, \rm{lim}}$. 
We find this $M_{g, \rm{lim}}( 0.8 < z < 1.0)$ to be, conservatively, $M_{g} = -20.75$. 
With this value we then calculate the rest of the $M_{g, \rm{lim}}$s by finding the
$M_{g}$ value where the cumulative number density ordered by absolute magnitude of the redshift bins 
equals that of the the highest redshift bin at $M_{g, \rm{lim}}( 0.8 < z < 1.0)$. 
Note that when calculating the number densities, the number of galaxies takes into account the 
statistical weights (described in Section \ref{sec:primus} and \ref{sec:sdss}).

For the EDP of the SDSS-{\em GALEX} sample (hereafter simply referred to as the SDSS EDP), 
we do not use the parent sample of the data due to 
the geometry of the combined angular selection function of the SDSS VAGC and {\em GALEX}. 
Instead, since we are not interested in the $FUV, NUV$ values for the EDP, we just use the
SDSS VAGC where the SDSS-{\em GALEX} catalog is derived from. 
Furthermore, we impose a redshift limit $0.0375-0.145$ on the SDSS EDP sample as opposed 
to the redshift range of $0.01-0.2$ in \cite{Moustakas:20133aa}.
This is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright 
galaxies at $z \sim 0.01$. 
In other words, the lower bound for the redshif range was empirically determined by the bright limit of 
the $M_{g}$ versus redshift distribution and the upper bound by the faint limit of the 
$M_{g}$ versus redshift distribution. 
The same fixed cumulative number density method is used on this SDSS EDP. 
By using a fixed cumulative number density method of 
Ultimately we use $M_{g,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins 
$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively. 
These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots the absolute magnitude versus the redshift for the EDP galaxies and the target galaxies. 
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:targetEDP}
        \epsscale{1.0}
        \plotone{absmag_redshift_target_EDP_sdss00375-0145_primus02-10.png}
        \caption{Absolute magnitude $M_{g}$ vs. redshift for the target galaxy population (black) with the Environment Defining Population (red) plotted on top. Both samples are divided into redshift bins:$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. The target galaxy population is stellar mass complete (Section \ref{sec:target} while the EDP is volume limited through $M_{g}$ limits (Section \ref{sec:environment}).}
    \end{center}
\end{figure*}

@@

\subsection{Edge Effects} \label{sec:edgeeffect}
One of the challenges in obtaining the galaxy environment using a fixed aperture method is accounting for the edge effects of the survey.
For the target galaxies located near the edge of the survey, part of the fixed aperture encompassing it will lie outside the survey regions. 
In this case, the $n_{env}$ will only reflect the galaxies which lie in the fraction of the aperture contained within the survey geometry.

@@

$V_{\rm{max},i}$ is the maximum cosmological volume where it is possible to observe each galaxy $i$ given the apparent magnitude limits of the survey.
However in Section \ref{sec:edgeffect} we remove the galaxies that lie on the edge of from the target sample. 
In doing so we reduce the maximum cosmological volume where a galaxy can be observed, thereby reducing $V_{\rm{max},i}$ to a what we will refer to as $V_{\rm{max,avail},i}$.

@@

The figures and analysis described in this paper are done using galaxy environment determined from a fixed aperture with $r_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.
The same analysis was repeated for various aperture dimensions: $r_{\rm{ap}} = 0.5, 1, 2, 3 \rm{Mpc}$ and $h_{\rm{ap}} = 25, 50 \rm{Mpc}$. 
Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
The results obtained from using these different are consistent with the results displayed in this paper. 
\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{QFfit_cylr1h50_PRIMUS_nbin6_SDSS_nbin2_z00-10_slope-yint-err-fit_mass_100-115_105fidmass_01massbin.png}
        \label{fig:qf}
        \caption{Quiescent fraction at fiducial mass $\rm{log} (\mathcal{M}/\mathcal{M}_{\odot}) = 10.5$ for low (triangle), mid (square) and high (circle) environments in redshift bins: $0.06-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$. Comparing these linear fit values in the redshift range for the different environment densities suggest that the change in QFs is indepdent of environment density.}
    \end{center}
\end{figure}

@@

\section{Appendix}
\subsection{Stellar Mass Function} \label{sec:smf_const}
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{smf_cylr2h50_thresh75_PRIMUS_nbin20_SDSS_nbin5_006_0145_smf_massbin03_jackknife.png}
        \caption{SMF and QF for $r_{\rm{ap}}=2 \rm{Mpc}$ and $h_{\rm{ap}}=50 \rm{Mpc}$}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{QFfit_cylr2h50_PRIMUS_nbin20_SDSS_nbin5_z00-10_slope-yint-err-fit_mass_100-110_105fidmass_01massbin.png}
        \label{fig:qf}
        \caption{QF at fiducial mass for $r_{\rm{ap}}=2 \rm{Mpc}$ and $h_{\rm{ap}}=50 \rm{Mpc}$}
    \end{center}
\end{figure*}

>>>>

\title{PRIMUS: Quiescent Fraction as a Function of Environment and Redshift}
\author{ChangHoon Hahn, Michael Blanton, Alison Coil, Richard Cool, Daniel Eisenstein, John Moustakas, Ken Wong, Guangtun Zhu}

\begin{abstract}
We examine the evolution of the quiescent fraction (QF) for galaxies in 
different density environments from $z=0.2-0.8$ using spectroscopic 
redshift and multi-wavelength imaging data from PRism MUlti-object 
Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). Using this 
data we construct a stellar mass limited target galaxy population of 
$40430$ galaxies from PRIMUS within redshift range $0.2-1.0$ and $106732$
galaxies from SDSS within redshift range $0.06-0.145$. This population 
is then classified as quiescent or star-forming using an evolving cut 
based on specific star-formation rate. The environment of the target 
population is then measured using a fixed cylindrical aperture method 
on a volume-limited {\em Environment Defining Population} constructed
from PRIMUS and SDSS.

Thresholds for the environment are imposed to classify the target galaxies as
high, mid, or low environments. For the quiescent and star-forming 
target galaxies we calculate the stellar mass functions in different environments and redshift.
Afterwards, we compute the QFs using the SMFs for the different environment 
and redshift ranges.  Comparing the QFs in these environment and redshift bins, we find the 
QF increases over cosmic time (decrease in redshift); however, the change of 
the QFs for the different environments are independent of the 
environment of galaxies. 
\end{abstract}

@@

\begin{table*} %Subject to significant change based on the classification of environment
  \caption{Summary of Galaxy Subsample}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
  Survey    &Redshift ($z$) &Density        &Quiescent $N_{\rm{g}}$ &Star-forming $N_{\rm{g}}$  \\ \hline 
  SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
            &               &Mid            &3614                       &4438                           \\
            &               &Low            &5419                       &8927                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
            &               &Mid            &177                    &403                          \\
            &               &Low            &768                    &2516                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
            &               &Mid            &195                       &405                           \\
            &               &Low            &871                       &2385                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
            &               &Mid            &186                       &327                           \\
            &               &Low            &833                       &1847                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
            &               &Mid            &94                       &163                           \\
            &               &Low            &373                       &810                           \\
            &               &               &                       &                           \\ \hline
  \multicolumn{5}{l}{}                                             \\       
    \end{tabular} 
  \end{center}
\end{table*}

@@

In all of the PRIMUS target fields we have near-UV (NUV) and far-UV (FUV) measurements from the {\em GALEX} Deep Imaging Survey (DIS; \cite{Martin:2005aa}; \cite{Morrissey:2005aa}). 
To minimize contamination from neighboring sources, we use a Bayesian photometric code EM$_{\rm{PHOT}}$ (based on expectation maximization algorithm of \cite{Guillaume:2006aa}). 
Furthermore, we use ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs in each of the fields to obtain integrated fluxes in all 
photometric bands.
To summarize, the general strategy employed is to use a circular aperture photometry to constrain the shape of the SED and then fixing the overall normalization to 
a estimate of the total magnitude in the detection band. 
\cite{Moustakas:2013aa} provides a detailed description of the calculation for each of our target fields.

From the spectroscopic redshift and photometry described above, we use \texttt{iSEDfit} to determine stellar masses, star formation rates (SFRs) and other physical properties
in a simplified Bayesian framework.
\texttt{iSEDfit}, which we will only briefly mention in this paper is discussed in detail in Appendix A of \cite{Moustakas:2013aa}.
The code uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. 
These generated model SEDs depend on population synthesis models and prior parameters.
In order to derive our fiducial stellar masses and star formation rates, we use the Flexible Stellar Population Synthesis (FSPS) models (\cite{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF. 
Other prior parameters are listed in Section 4.1 of \cite{Moustakas:2013aa}. 
The photometric bands we use for the fitting in our PRIMUS data are the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$, and the five optical bands
(in the COSMOS field, we fit seven optical bands and near-infrared bands, see Section 2.3 of \cite{Moustakas:2013aa}).
For a more detailed description of the data used in this paper, we refer readers to \cite{Moustakas:2013aa} Section 2 and Section 4.1.

\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:targetEDP}
        \epsscale{1.0}
	\plotone{fig_EDP_absmag_redshift.png}
        \caption{Absolute magnitude $M_{r}$ vs. redshift for the target galaxy population (black) with the Environment Defining Population (red) plotted on top. Both samples are divided into redshift bins:$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. The target galaxy population is stellar mass complete (Section \ref{sec:target} while the EDP is volume limited through $M_{g}$ limits (Section \ref{sec:environment}).}
    \end{center}
\end{figure*}

\subsection{SDSS-GALEX} \label{sec:sdss}
For galaxies at low redshifts we use the SDSS Data Release 7 (DR7; \cite{Abazajian:2009aa}). 
From the SDSS DR7 data, which provides high fidelity $ugriz$ photometry and spectroscopic redshift, we specifically use galaxies from the New York University 
Value-Added Galaxy Catalog that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ 
and spectroscopic redshits $0.01<z<0.2$ (\cite{Blanton:2005aa}). 
Within this sample, we select galaxies with medium depth observations from GALEX. 
This is done by first retrieving the positions of all {\em GALEX} tiles from GALEX Release 6 with total exposure time greater than $1$ ks and then constructing 
a joint angular selection function of the SDSS-{\em GALEX} Sample. 
This results in a final sample of $167,727$ SDSS galaxies with {\em GALEX} imaging.

For this final sample, we use the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diamater search radius to obtain the NUV and FUV photometry. 
For the optical photometry we use $ugriz$ bands (from the SDSS \texttt{model} magnitudes) scaled to the $r$-band \texttt{cmodel} magnitude. 
We supplement the above UV and optical photometry with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \cite{Jarrett:2000aa}) and with photometry at $3.4$ 
and $4.6 \mu \rm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}. 
Further details on the photometry of the SDSS data used in this paper is provided in \cite{Moustakas:2013aa} Section 2.4.

To obtain the stellar masses and SFRs for the SDSS data, we use \texttt{iSEDfit} as done in Section \ref{sec:primus}. 
Except we use twelve photometric bands: {\em GALEX} FUV and NUV, SDSS $ugriz$, 2MASS $JHK_{s}$, and WISE $3.4$ and $4.6 \mu \rm{m}$.
\subsection{Galaxy Samples} \label{sec:target} 
In this seciton we will define the galaxy sample we use for our SMFs and QFs.
The population at intermediate redshift is derived from the PRIMUS data and the population at low redshift is derived from the SDSS data, both described above.
For the intermediate redshift target galaxy population, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for its parent sample.
We take the statistically complete {\em primary} sample from the PRIMUS data, \cite{Coil:2011aa}, and then we impose magnitude limits on optical selection bands as specified in 
\cite{Moustakas:2013aa} Table 1.
These limits are in different optical selection bands and have different values for our five PRIMUS target fields.
Next, we join the PRIMUS, {\em GALEX}, and IRAC window functions to construct the angular selection function.
We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$) within the 
redshift range $0.2 - 1.0$.
Afterwards we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) to the objects in order to correct for targeting incompleteness and redshift 
failures.
The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
Equation 1 in \cite{Moustakas:2013aa}.
In addition to the selection criteria above, we impose stellar mass limits to have a stellar mass complete sample.  
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, apparent magnitude limit of the survey, and the typical stellar 
mass-to-light ratio of galaxies near the flux limit.

@@

For our target galaxy population at low redshift we use our SDSS-{\em GALEX} data. 
We limit our target population within the redshift range $0.06-0.145$ due to redshift limits later imposed for the volume-limited Environment Defining Population (\ref{sec:environment}).
The NYU-VAGC provides statistical weight estimates for targeting completeness.
In order to have a stellar mass complete low redshift target population, we use a uniform stellar mass limit of $10^9 \mathcal{M}_{\odot}$, which is above the surface 
brightness and stellar mass-to-light ratio completness limits (\cite{Blanton:2005ab}; \cite{Baldry:2008aa}).
The absolute magnitude ($M_g$) versus redshift for the target galaxy population at both low redshift and intermediate redshift is plotted in Figure \ref{fig:targetEDP}.
We again refer readers to \cite{Moustakas:2013aa} for details; more specifically, Figure 2., Sections 3.1, and 4.3.

@@

In order to obtain the fixed aperture based environment for the galaxies in the target population, 
we first establish a volume limited {\it Environment Defining Population} (EDP) by imposing a fixed 
cumulative number density absolute magnitude cut off. 
By using a fixed cumulative number density for this sample we seek to build an EDP with galaxies that 
have similar populations in all of the redshift bins i.e. accounting for the progenitor bias. 
As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find in their analysis of the cumulative number density 
method using a dark matter simulation with abundance matching and a semi-analytic model, respectively, 
cumulative number density method, while it does not precisely account for the scatter in mass accretion or 
galaxy-galaxy mergers, provides a promising tool to compare galaxy populations over a wide range of cosmic time.
In addition we use the highest redshift bin cumulative number density as the fixed number density 
%%%FINISH THIS SENTENCE
Furthermore \cite{Behroozi:2013aa}

\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{fig_smf_cylr2h25_thresh75_bin0_25.png}
        \caption{Stellar mass functions and quiescent fraction for galaxies in the $30$ subsamples divided into redshift bins, $0.06-0.145$ (green), $0.2-0.4$ (red), $0.4-0.6$ 
(magenta), $0.6-0.8$ (blue), and $0.8-1.0$ (black) with low, mid, and high environments. The environments were classified using cylindrical aperture of $R=1\rm{Mpc}$ and $H=50\rm{Mpc}$ 
with environment classification thresholds specified in Table \ref{tab:aperture}. The mass bins for the SMFs and QFs have widths $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.3$. 
SMFs for subsamples with the same environment density classification are plotted on panels along the same column: low (left), mid (middle), and high (right) environments. The top
panels plot SMFs for subsamples with star forming galaxies. The middle panels plot the SMFs for subsamples with quiescent galaxies. The bottom panels plot the QFs for the 
corresponding star-forming SMFs and quiescent SMFs in the same environment classification and redshift bin.}
    \end{center}
\end{figure*}

The EDP for the PRIMUS sample is derived from the same parent sample as the target galaxies. 
We restrict the PRIMUS EDP galaxies within the redshift range $0.2-1.0$ and divide them into redshift bins of width $\Delta z = 0.2$. 
For each of these redshift bins, we impose separate absolute magnitude ($M_{g,\rm{lim}}$) limits such 
that the cumulative number density of the sample ordered by $M_{g}$ is equal to the cumulative 
number density of the highest redshift bin with an empirically determined limit. 
First, to determine the highest redshift bin ($0.8-1.0$) limit we look at the $M_{g}$ distribution with bin size
$\Delta M_{g} = 0.25$ and select $M_{g,\rm{lim}}$ to be the $M_{g}$ value near the peak of the 
distribution where number density of the bins with fainter objects (greater $M_{g}$ value) are smaller
than the number density of the bin at $M_{g, \rm{lim}}$. 
We find this $M_{g, \rm{lim}}( 0.8 < z < 1.0)$ to be, conservatively, $M_{g} = -20.75$. 
With this value we then calculate the rest of the $M_{g, \rm{lim}}$s by finding the
$M_{g}$ value where the cumulative number density ordered by absolute magnitude of the redshift bins 
equals that of the the highest redshift bin at $M_{g, \rm{lim}}( 0.8 < z < 1.0)$. 
Note that when calculating the number densities, the number of galaxies takes into account the 
statistical weights (described in Section \ref{sec:primus} and \ref{sec:sdss}).

For the EDP of the SDSS-{\em GALEX} sample (hereafter simply referred to as the SDSS EDP), 
we do not use the parent sample of the data due to 
the geometry of the combined angular selection function of the SDSS VAGC and {\em GALEX}. 
Instead, since we are not interested in the $FUV, NUV$ values for the EDP, we just use the
SDSS VAGC where the SDSS-{\em GALEX} catalog is derived from. 
Furthermore, we impose a redshift limit $0.0375-0.145$ on the SDSS EDP sample as opposed 
to the redshift range of $0.01-0.2$ in \cite{Moustakas:20133aa}.
This is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright 
galaxies at $z \sim 0.01$. 
In other words, the lower bound for the redshif range was empirically determined by the bright limit of 
the $M_{g}$ versus redshift distribution and the upper bound by the faint limit of the 
$M_{g}$ versus redshift distribution. 
The same fixed cumulative number density method is used on this SDSS EDP. 
Ultimately we use $M_{g,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins 
$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively. 
These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots the absolute magnitude versus the redshift for the EDP galaxies and the target galaxies.

@@

\subsection{Edge Effects} \label{sec:edgeeffect}
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{fig_qf_cylr2h25_thresh75_bin0_25.png}
        \caption{Quiescent fraction for galaxies in the $30$ subsamples divided into redshift bins, $0.06-0.145$ (green), $0.2-0.4$ (red), $0.4-0.6$ 
(magenta), $0.6-0.8$ (blue), and $0.8-1.0$ (black) with low, mid, and high environments. The environments were classified using cylindrical aperture of $R=1\rm{Mpc}$ and $H=50\rm{Mpc}$ 
with environment classification thresholds specified in Table \ref{tab:aperture}. The mass bins for the SMFs and QFs have widths $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.3$. 
SMFs for subsamples with the same environment density classification are plotted on panels along the same column: low (left), mid (middle), and high (right) environments. The top
panels plot SMFs for subsamples with star forming galaxies. The middle panels plot the SMFs for subsamples with quiescent galaxies. The bottom panels plot the QFs for the 
corresponding star-forming SMFs and quiescent SMFs in the same environment classification and redshift bin.}
    \end{center}
\end{figure*}

One of the challenges in obtaining the galaxy environment using a fixed aperture method is accounting for the edge effects of the survey.
For the target galaxies located near the edge of the survey, part of the fixed aperture encompassing it will lie outside the survey regions. 
In this case, the $n_{env}$ will only reflect the galaxies which lie in the fraction of the aperture contained within the survey geometry.

@@

$V_{\rm{max},i}$ is the maximum cosmological volume where it is possible to observe each galaxy $i$ given the apparent magnitude limits of the survey.
However in Section \ref{sec:edgeeffect} we remove the galaxies that lie on the edge of from the target sample. 
In doing so we reduce the maximum cosmological volume where a galaxy can be observed, thereby reducing $V_{\rm{max},i}$ to a what we will refer to as $V_{\rm{max,avail},i}$.

@@

The figures and analysis described in this paper are done using galaxy environment determined from a fixed aperture with $r_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.
The same analysis was repeated for various aperture dimensions: $r_{\rm{ap}} = 0.5, 1, 2, 3 \rm{Mpc}$ and $h_{\rm{ap}} = 25, 50 \rm{Mpc}$. 
Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
The results obtained from using these different are consistent with the results displayed in this paper. 
\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{fig_qffit_cylr2h25_thresh75_bin0_25.png}
        \label{fig:qf}
        \caption{Quiescent fraction at fiducial mass $\rm{log} (\mathcal{M}/\mathcal{M}_{\odot}) = 10.5$ for low (triangle), mid (square) and high (circle) environments in redshift bins: $0.06-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$. Comparing these linear fit values in the redshift range for the different environment densities suggest that the change in QFs is indepdent of environment density.}
    \end{center}
\end{figure}

@@

\appendix
\begin{table*} %Will contain much more information on environments. 
  \caption{Fixed Cylindrical Aperture Dimensions}
  \label{tab:aperture}
  \begin{center}
    \leavevmode
    \begin{tabular}{llllll} \hline \hline              
  Radius (Mpc)          &Height (Mpc)      &$n_{bin}$   &Edgecut &High Env Threshold (galaxies) &Low Env Threshold (galaxies) \\ \hline 
  1.0 &50 &6 & 80\% & 1.5 & 0.0          \\
  2.0 &50 &6 & 75\% & 4.0 & 0.0          \\ \hline
  \multicolumn{6}{l}{}                                             \\       
    \end{tabular}
  \end{center}
\end{table*}

\subsection{Stellar Mass Function} \label{sec:smf_const}
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{fig_smf_cylr1h25_thresh80_bin0_25.png}
        \caption{SMF for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{fig_qf_cylr1h25_thresh80_bin0_25.png}
        \caption{QF for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{fig_qffit_cylr1h25_thresh80_bin0_25.png}
        \label{fig:qf}
        \caption{QF at fiducial mass for $r_{\rm{ap}}=2 \rm{Mpc}$ and $h_{\rm{ap}}=50 \rm{Mpc}$}
    \end{center}
\end{figure*}
